Carbonate chemistry at Ny-Ålesund: AWIPEV-CO~2~ Project

### 2021-01-29 awipev-CO2.Rmd
dunno

#################### Regression function
# function regression plot with model II equation (MA) in title
## Dans labs ajout de la variable TITRE pour mettre titre avant chaque graphe
ggreg2 <- function (fit, xdata, ydata) { # x and y are the names of the variables
  fit_data <- data.frame(fit$x, fit$y)
  colnames(fit_data) = c(xdata, ydata)
reg <- fit$regression.results[2,] #one selects MA only
intercept <- reg$Intercept
slope <- reg$Slope
  ggplot(data = fit_data, aes_string(x = xdata, y = ydata)) + 
  geom_point(size = 2, col = "blue") +
  geom_abline(aes(intercept = fit$regression.results[2,2], slope = fit$regression.results[2,3]),
              colour = "blue")  + 
  labs(title = paste(titre,"\n Adj R2 = ", signif(fit$rsquare, 3),
                     "; Intercept =", signif(intercept, 3),
                     "; Slope =", signif(slope, 3),
                     "; P =", signif(fit$P.param, 3)))
}

#################### Function RMSE for model 2 regression root mean square error
lm2 <- function(x, y) { 
  fit <- lmodel2(y  ~ x , nperm = 99)
  intercept <- fit$regression.results[2,2]
  slope <- fit$regression.results[2,3]
  predicted <- intercept + x * slope
  error <- predicted - x
  my_list <- list(fit = fit, rmse = sqrt(mean(error^2, na.rm=TRUE)))
  return(my_list)
  }

@@

p <-  ggplot(d_all,aes(x=pco2_calc_fb, y= pco2_fb, label = monthd))+
   geom_text(aes(color = factor(monthd)))+
  scale_color_discrete(guide="none")+
  geom_abline(slope = 1, intercept = 0, linetype = "dashed") +
  geom_abline(aes(intercept = fit$regression.results[2,2], slope = fit$regression.results[2,3]),colour = "blue") +
  labs(title = paste(title,"\n Adj R2 = ", signif(fit$rsquare, 3),
                     "; Intercept =", signif(fit$regression.results[2,2], 3),
                     "; Slope =", signif( fit$regression.results[2,3], 3),
                     "; P =", signif(fit$P.param, 3))) +
  theme(aspect.ratio=1,plot.title = element_text(size=7)) + 
  coord_fixed(ratio = 1 ,xlim=c(200,460) , ylim=c(200,460))+
  labs(x="Calculated pCO2", y="Contros pCO2 corrected", color = "Months") + theme_bw()  
```
The relationship between the Contros and calculated *p*CO~2~ is not good at all in the sense that it is far from the 1:1 line, despite a good r2 (`r round(fit$rsquare, digits=2)`).
```{r plot measured vs calculated pCO2, echo=FALSE, warning=FALSE, message=FALSE, out.width='100%', fig.align="center"}
print(p) # pco2_calc_fb_pco2_corr_text
```

>>>>

#################### Regression function
# function regression plot with model II equation (MA) in title
## Dans labs ajout de la variable TITRE pour mettre titre avant chaque graphe
ggreg2 <- function (fit, xdata, ydata) { # x and y are the names of the variables
  fit_data <- data.frame(fit$x, fit$y)
  colnames(fit_data) = c(xdata, ydata)
reg <- fit$regression.results[2,] #one selects MA only
intercept <- reg$Intercept
slope <- reg$Slope
  ggplot(data = fit_data, aes_string(x = xdata, y = ydata)) + 
  geom_point(size = 2, col = "blue") +
  geom_abline(aes(intercept = fit$regression.results[2,2], slope = fit$regression.results[2,3]),
              colour = "blue")  + 
  labs(title = paste(title,"\n Adj R2 = ", signif(fit$rsquare, 3),
                     "; Intercept =", signif(intercept, 3),
                     "; Slope =", signif(slope, 3),
                     "; P =", signif(fit$P.param, 3)))
}

#################### Function RMSE for model 2 regression root mean square error
lm2 <- function(data = NULL, x, y) {
  xs <- deparse(substitute(x))
  ys <- deparse(substitute(y))
#fit <- lmodel2(formula = y  ~ x, data = data, nperm = 99)
  print(y)
  #return(fit)

  lmwrap <- function(d,y,x) {
    ys <- deparse(substitute(y))
    xs <- deparse(substitute(x))
    f <- reformulate(xs,response=ys)
    return(lm(f,data=d))
}
mydata <- data.frame(X=1:10,Y=rnorm(10))
lmwrap(mydata,Y, X)

lm2(x = d_all$pco2_calc_fb, y = d_all$pco2_fb)
lm2(data = d_all, x=pco2_calc_fb, y=pco2_fb)

lmodel2(d_all$pco2_calc_fb ~ d_all$pco2_fb, nperm = 99)

  intercept_MA <- fit$regression.results[2,2]
  slope_MA <- fit$regression.results[2,3]
  intercept_OLS <- fit$regression.results[1,2]
  slope_OLS <- fit$regression.results[1,3]
  predicted <- intercept_OLS + df[[x]] * slope_OLS
  error <- x - predicted
  my_list <- list(fit = fit, rmse = sqrt(mean(error^2, na.rm=TRUE)))
  return(my_list)
  }

@@

p <-  ggplot(d_all,aes(x=pco2_calc_fb, y= pco2_fb, label = monthd))+
   geom_text(aes(color = factor(monthd)))+
  scale_color_discrete(guide="none")+
  geom_abline(slope = 1, intercept = 0, linetype = "dashed") +
  geom_abline(aes(intercept = fit$regression.results[2,2], slope = fit$regression.results[2,3]),colour = "blue") +
  labs(title = paste(title,"\n Adj R2 = ", signif(fit$rsquare, 3),
                     "; Intercept =", signif(fit$regression.results[2,2], 3),
                     "; Slope =", signif( fit$regression.results[2,3], 3),
                     "; P =", signif(fit$P.param, 3))) +
  theme(aspect.ratio=1,plot.title = element_text(size=7)) + 
  coord_fixed(ratio = 1 ,xlim=c(200,460) , ylim=c(200,460))+
  labs(x="Calculated pCO2", y="Contros pCO2") + theme_bw()  
```
The relationship between the Contros and calculated *p*CO~2~ is not good at all in the sense that it is far from the 1:1 line, despite a good r2 (`r round(fit$rsquare, digits=2)`).
```{r plot measured vs calculated pCO2, echo=FALSE, warning=FALSE, message=FALSE, out.width='100%', fig.align="center"}
print(p) # pco2_calc_fb_pco2_corr_text
```
